---
title: "Wheat Price vs Wages"
output: html_document
---

Displayed is Playfair's 1821 data showing wheat prices and laborers' weekly wages.

Generated April 22, 2017.

```{r}
library(HistData)
library(plotly)
```

## Original graph

Playfair's original graph resembled the following - it "commits the sin" of showing
two Y variables on different axes.

```{r}
x <- list(title="Year")
y <- list(title="Wheat Price vs Wages")
plot_ly(Wheat) %>% layout(xaxis=x, yaxis=y) %>% add_trace(x = ~Year, y = ~Wheat, mode="lines") %>% add_trace(x = ~Year, y = ~Wages, mode="lines")
```

## Graphing ratios instead
The intuition to instead show the ratio of wheat
prices to wages would not occur for another 50 years. This more
clearly shows the "units of wheat" one can buy with their wage
increasing:

```{r}
Wheat$ratio <- Wheat$Wages / Wheat$Wheat
x <- list(title="Year")
y <- list(title="Wheat Price vs Wages")
plot_ly(Wheat) %>% layout(xaxis=x, yaxis=y) %>% add_trace(x = ~Year, y = ~ratio, mode="lines")
```